MCC Kids Model Predictions

### 2019-03-06 stats/kids/kids_model_predictions.Rmd
adult models for paper first pass

                                   ))))%>%
  select(Speaker,age_num,Alignment,so,priorProbs,correct_inf)

@@

  var noise_slope = uniformDrift({a: -2, b: 2, width: 0.2})
  var noise_int = uniformDrift({a: -2, b: 2, width: 0.2})

@@

    var noise = logistic(noise_int + noise_slope * (row.age_num))

@@

dev_noisy_pred <- dev_noisy_model_pred %>%
  filter(!(Parameter %in% c("noise_int", "noise_slope"))) %>%
  separate(Parameter, into = c("age", "Speaker", "Alignment"), sep="/")%>%
  mutate( model = "developmental noise parameter")%>%
  group_by(model, age,Alignment,Speaker) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper =hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))

>>>>

                                   ))))%>%
  ungroup()%>%
  mutate(min_age = min(age_num))%>%
  select(Speaker,age_num,min_age,Alignment,so,priorProbs,correct_inf)

@@

  var noise_slope = uniformDrift({a: -2, b: 2, width: 0.4})
  var noise_int = uniformDrift({a: -2, b: 2, width: 0.4})

@@

    var noise = logistic(noise_int + noise_slope * (row.age_num-row.min_age))

    //display(JSON.stringify(noise))

@@

dev_noisy_pred <- dev_noisy_model_pred %>%
  filter(!(Parameter %in% c("noise_int", "noise_slope"))) %>%
  separate(Parameter, into = c("age", "Speaker", "Alignment"), sep="/")%>%
  mutate( model = "developmental noise parameter")%>%
  group_by(model, age,Alignment,Speaker) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper =hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))
```

x <- data_frame(
  age = rep(seq(0,2, by = 0.05),8),
  param = c(rep("-2/-2",41),rep("-2/-1",41),rep("-1/-1",41),rep("-1/0",41),rep("0/-1",41),rep("1/1",41),rep("2/1",41),rep("2/2",41)),
  int = c(rep(-2,41),rep(-2,41),rep(-1,41),rep(-1,41),rep(0,41),rep(1,41),rep(2,41),rep(2,41)),
  slope = c(rep(-2,41),rep(-1,41),rep(-1,41),rep(0,41),rep(-1,41),rep(1,41),rep(1,41),rep(2,41))
) %>%
  mutate(y = plogis(int + slope *age))

ggplot(x, aes(x = age, y= y,col = param))+
  geom_line()+
  ylim(0,1)
